---
title: "FSIpkg"
author: "Richard Amegble"
date: "2024-10-14"
output: github_document
---

## Introduction

This package allows to extract [Fragile States Index](https://fragilestatesindex.org/). `read_fsi` is built to perform this extraction. There are another two functions that help to find the country name and series names. 

## Install package 
```{r, warning=FALSE, message=FALSE}
#devtools::install_github("Dzigbodi/FSIpkg")
```

```{r}
library(FSIpkg)
```

## List of series 

```{r}
head(fsi_series())
```
## List of Countries 

```{r}
print(fsi_countries())
```
## Extraction between period

```{r}
df <- read_fsi( startyear=2023, endyear = 2024)
print(head(df))
```


## Extraction list of countries
```{r}
country_list <- c("Togo", "Canada", "Ghana")
df_country <- read_fsi(startyear=2020, endyear = 2021,country = country_list )
print(head(df_country))
```

## Remove the Rank and Total from the extraction
```{r}
df <- read_fsi(startyear=2020, endyear = 2021,country = country_list ,rank = F, total = F)
print(head(df))
```

## Extraction of the whole data

```{r}
df <- read_fsi()
print(head(df))
```

